---
title: "K-S testing"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)
```

```{r packages}
library(tidyverse)
library(flextable)
library(readxl)
library(extrafont)
library(forcats)
library(writexl)
library(car)
library(moments)
```

```{r table-function}
#times new roman tables
my_ft_theme <- function(ft, ...) {
  # Remove vertical cell padding
  ft <- padding(ft, padding.top = 0, padding.bottom = 0, part = "all")
  
  # Change font to TNR 11
  ft <- font(ft, fontname = "Times New Roman", part = "all")
  ft <- fontsize(ft, part = "all", size = 12)
  ft
}
```


```{r}
headscan_full1<-read_excel("C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\headscan_full1.xlsx")
str(headscan_full1)
```

Skewness is a measure of the asymmetry of a distribution. This value can be positive or negative.

A negative skew indicates that the tail is on the left side of the distribution, which extends towards more negative values.
A positive skew indicates that the tail is on the right side of the distribution, which extends towards more positive values.
A value of zero indicates that there is no skewness in the distribution at all, meaning the distribution is perfectly symmetrical.
Kurtosis is a measure of whether or not a distribution is heavy-tailed or light-tailed relative to a normal distribution.

The rule of thumb seems to be: If the skewness is between -0.5 and 0.5, the data are fairly symmetrical. If the skewness is between -1 and – 0.5 or between 0.5 and 1, the data are moderately skewed. If the skewness is less than -1 or greater than 1, the data are highly skewed.

The kurtosis of a normal distribution is 3.
If a given distribution has a kurtosis less than 3, it is said to be playkurtic, which means it tends to produce fewer and less extreme outliers than the normal distribution.
If a given distribution has a kurtosis greater than 3, it is said to be leptokurtic, which means it tends to produce more outliers than the normal distribution.

```{r, fig.height=5.5, fig.width=7.5}
AA_Cx <- headscan_full1$AA_C

kurtosis(AA_Cx, na.rm = TRUE)

skewness(AA_Cx, na.rm = TRUE)

nortest::lillie.test(AA_Cx)

hist(AA_Cx, breaks=30)

qqnorm(AA_Cx)
qqline(AA_Cx)

qqPlot(AA_Cx, distribution = "norm")


```
```{r}
kurtosis(headscan_full1$AA_C, na.rm = TRUE)
```

