---
title: "running-MANOVA"
output: html_document
date: "2022-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(readxl)
library(officer)
library(flextable)
library(extrafont)
library(writexl)
library(rstatix)
library(corrr)
library(corrplot)
library(car)
library(heplots)
library(broom)
library(emmeans)
```

```{r}
#times new roman tables
my_ft_theme <- function(ft, ...) {
  # Remove vertical cell padding
  ft <- padding(ft, padding.top = 0, padding.bottom = 0, part = "all")
  
  # Change font to TNR 11
  ft <- font(ft, fontname = "Times New Roman", part = "all")
  ft <- fontsize(ft, part = "all", size = 12)
  ft
}
```

```{r}

chosen_nona1 <- read_excel("C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\chosen_nona1.xlsx")

variables <- cbind(chosen_nona1$AA_C, chosen_nona1$BiW_C, chosen_nona1$BiW_L, 
                   chosen_nona1$GoSub_C, chosen_nona1$NRB_L, chosen_nona1$ProS_L,
                   chosen_nona1$SelP_L, chosen_nona1$SelM_L, chosen_nona1$SnasM_C,
                   chosen_nona1$TrSman_C, chosen_nona1$TrTr_C, chosen_nona1$TrTr_L)
```

#https://www.hindawi.com/journals/cmmm/2019/2173638/ 
Use Pillai! better for when we don't know enough about covariance

#https://www.sagepub.com/sites/default/files/upm-assets/9761_book_item_9761.pdf
Type III sum of squares can be used in models where there are uneven group sizes, although there needs to be at least one participant in each cell. It calculates the sum of squares after the independent variables have all been adjusted for the inclusion of all other independent variables in the model


```{r}
output<-lm(variables ~ gender+race_eth+age_group, data=chosen_nona1,
           contrasts = list(gender=contr.sum, race_eth=contr.sum, age_group=contr.sum))

manova_out_nona1 <- Manova(output, type="III")

summary(manova_out_nona1)
```


```{r}
output1<-manova(variables ~ gender+race_eth+age_group, data=chosen_nona1)

#type 3 and type 1 give same Pillai values

summary(output1)
```


```{r}
output2<-as.data.frame(tidy(output1))

output2$p.value <- formatC(output2$p.value, format = "e")

output2 <- rename(output2, f.statistic = statistic)

#Autofit Width Table TNR
flextable(output2) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Additive MANOVA Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```

```{r}
AA_Cout <- aov(AA_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(AA_Cout)
AA_Cout_data <- as.data.frame(tidy(AA_Cout))
```

```{r}
AA_Cout_data <- rename(AA_Cout_data, f.statistic = statistic)
AA_Cout_data$p.value <- formatC(AA_Cout_data$p.value, format = "e")

#Autofit Width Table TNR
flextable(AA_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("AA_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
emmeans(AA_Cout, ~ gender)
emmip(AA_Cout, ~ gender)
```
```{r}
emmeans(AA_Cout, ~ race_eth)
emmip(AA_Cout, ~ race_eth)
```
```{r}
emmeans(AA_Cout, ~ age_group)
emmip(AA_Cout, ~ age_group)
```




```{r}
BiW_Lout <- aov(BiW_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(BiW_Lout)
BiW_Lout_data <- as.data.frame(tidy(BiW_Lout))
```

```{r}
BiW_Lout_data <- rename(BiW_Lout_data, f.statistic = statistic)
BiW_Lout_data$p.value <- formatC(BiW_Lout_data$p.value, format = "e")

#Autofit Width Table TNR
flextable(BiW_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("BiW_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
emmeans(BiW_Lout, ~ gender)
emmip(BiW_Lout, ~ gender)
```
```{r}
emmeans(BiW_Lout, ~ race_eth)
emmip(BiW_Lout, ~ race_eth)
```
```{r}
emmeans(BiW_Lout, ~ age_group)
emmip(BiW_Lout, ~ age_group)
```


```{r}
BiW_Cout <- aov(BiW_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(BiW_Cout)
BiW_Cout_data <- as.data.frame(tidy(BiW_Cout))
```

```{r}
BiW_Cout_data <- rename(BiW_Cout_data, f.statistic = statistic)
BiW_Cout_data$p.value <- formatC(BiW_Cout_data$p.value, format = "e")

#Autofit Width Table TNR
flextable(BiW_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("BiW_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
emmeans(BiW_Cout, ~ gender)
emmip(BiW_Cout, ~ gender)
```
```{r}
emmeans(BiW_Cout, ~ race_eth)
emmip(BiW_Cout, ~ race_eth)
```


```{r}
GoSub_Cout <- aov(GoSub_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(GoSub_Cout)
GoSub_Cout_data <- as.data.frame(tidy(GoSub_Cout))
```

```{r}
GoSub_Cout_data <- rename(GoSub_Cout_data, f.statistic = statistic)
GoSub_Cout_data$p.value <- formatC(GoSub_Cout_data$p.value, format = "e")

#Autofit Width Table TNR
flextable(GoSub_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("GoSub_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
emmeans(GoSub_Cout, ~ gender)
emmip(GoSub_Cout, ~ gender)
```
```{r}
emmeans(GoSub_Cout, ~ race_eth)
emmip(GoSub_Cout, ~ race_eth)
```
```{r}
emmeans(GoSub_Cout, ~ age_group)
emmip(GoSub_Cout, ~ age_group)
```



```{r}
NRB_Lout <- aov(NRB_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(NRB_Lout)
NRB_Lout_data <- as.data.frame(tidy(NRB_Lout))
```

```{r}
NRB_Lout_data <- rename(NRB_Lout_data, f.statistic = statistic)
NRB_Lout_data$p.value <- formatC(NRB_Lout_data$p.value, format = "e")

#Autofit Width Table TNR
flextable(NRB_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("NRB_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
emmeans(NRB_Lout, ~ gender)
emmip(NRB_Lout, ~ gender)
```
```{r}
emmeans(NRB_Lout, ~ race_eth)
emmip(NRB_Lout, ~ race_eth)
```



```{r}
ProS_Lout <- aov(ProS_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(ProS_Lout)
ProS_Lout_data <- as.data.frame(tidy(ProS_Lout))
```

```{r}
ProS_Lout_data <- rename(ProS_Lout_data, f.statistic = statistic)
ProS_Lout_data$p.value <- formatC(ProS_Lout_data$p.value, format = "e")

#Autofit Width Table TNR
flextable(ProS_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("ProS_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
emmeans(ProS_Lout, ~ gender)
emmip(ProS_Lout, ~ gender)
```
```{r}
emmeans(ProS_Lout, ~ race_eth)
emmip(ProS_Lout, ~ race_eth)
```
```{r}
emmeans(ProS_Lout, ~ age_group)
emmip(ProS_Lout, ~ age_group)
```



