---
title: "K-S testing"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)
```

```{r packages}
library(tidyverse)
library(flextable)
library(readxl)
library(extrafont)
library(forcats)
library(writexl)
library(car)
library(moments)
library(PerformanceAnalytics)
```

```{r table-function}
#times new roman tables
my_ft_theme <- function(ft, ...) {
  # Remove vertical cell padding
  ft <- padding(ft, padding.top = 0, padding.bottom = 0, part = "all")
  
  # Change font to TNR 11
  ft <- font(ft, fontname = "Times New Roman", part = "all")
  ft <- fontsize(ft, part = "all", size = 12)
  ft
}
```


```{r}
headscan_full1<-read_excel("C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\headscan_full1.xlsx")
str(headscan_full1)
```

Skewness is a measure of the asymmetry of a distribution. This value can be positive or negative.

A negative skew indicates that the tail is on the left side of the distribution, which extends towards more negative values.
A positive skew indicates that the tail is on the right side of the distribution, which extends towards more positive values.
A value of zero indicates that there is no skewness in the distribution at all, meaning the distribution is perfectly symmetrical.
PerformanceAnalytics::PerformanceAnalytics::kurtosis is a measure of whether or not a distribution is heavy-tailed or light-tailed relative to a normal distribution.

The rule of thumb seems to be: If the skewness is between -0.5 and 0.5, the data are fairly symmetrical. If the skewness is between -1 and – 0.5 or between 0.5 and 1, the data are moderately skewed. If the skewness is less than -1 or greater than 1, the data are highly skewed.

The PerformanceAnalytics::kurtosis of a normal distribution is 3.
If a given distribution has a PerformanceAnalytics::kurtosis less than 3, it is said to be playkurtic, which means it tends to produce fewer and less extreme outliers than the normal distribution.
If a given distribution has a PerformanceAnalytics::kurtosis greater than 3, it is said to be leptokurtic, which means it tends to produce more outliers than the normal distribution.

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$AA_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$AA_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$AA_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$AA_C, na.rm = TRUE)
```


```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$BGl_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$BGl_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$BGl_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$BGl_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$BiW_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$BiW_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$BiW_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$BiW_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$BiW_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$BiW_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$BiW_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$BiW_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$ChCh_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$ChCh_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$ChCh_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$ChCh_C, na.rm = TRUE)
```


```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$GoSub_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$GoSub_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$GoSub_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$GoSub_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$NRB_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$NRB_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$NRB_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$NRB_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$ProA_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$ProA_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$ProA_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$ProA_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$ProA_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$ProA_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$ProA_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$ProA_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$ProS_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$ProS_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$ProS_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$ProS_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$ProS_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$ProS_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$ProS_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$ProS_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SelP_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SelP_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SelP_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SelP_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SelP_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SelP_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SelP_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SelP_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SelDH_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SelDH_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SelDH_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SelDH_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SelM_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SelM_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SelM_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SelM_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SnasM_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SnasM_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SnasM_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SnasM_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SnasM_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SnasM_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SnasM_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SnasM_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SmanM_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SmanM_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SmanM_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SmanM_L, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$SmanM_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$SmanM_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$SmanM_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$SmanM_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$TrHO_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrHO_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrHO_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrHO_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$TrEJ_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrEJ_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrEJ_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrEJ_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$TrGo_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrGo_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrGo_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrGo_C, na.rm = TRUE)
```

```{r, fig.height=5.5, fig.width=7.5}
qqPlot(headscan_full1$TrSel_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrSel_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrSel_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrSel_C, na.rm = TRUE)
```

```{r}
qqPlot(headscan_full1$TrSman_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrSman_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrSman_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrSman_C, na.rm = TRUE)
```

```{r}
qqPlot(headscan_full1$TrSnas_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrSnas_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrSnas_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrSnas_C, na.rm = TRUE)
```

```{r}
qqPlot(headscan_full1$TrTr_C, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrTr_C, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrTr_C, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrTr_C, na.rm = TRUE)
```

```{r}
qqPlot(headscan_full1$TrTr_L, distribution = "norm", col.lines = "grey")

hist(headscan_full1$TrTr_L, breaks = 30)

PerformanceAnalytics::kurtosis(headscan_full1$TrTr_L, na.rm = TRUE, method= "excess")

skewness(headscan_full1$TrTr_L, na.rm = TRUE)
```